\cvsection{Education}
\cvevent{BSc. Mechatronics Engineering}{The German University in Cairo}{2018}{Cairo}
\grad{Excellent with Honors}
\divider


\cvsection{Online Degrees}
\cvachievement{\faReddit}{Robotics Software Engineer Nanodegree}{
\href{https://confirm.udacity.com/USDS922J}{Certificate} --- \href{https://s3-us-west-2.amazonaws.com/udacity-printer/production/syllabus/syllabus-nd209-default-en-us.pdf}{Description}
\begin{itemize}
\item{ROS Essentials.}
\item{Localization.}
\item{Mapping and SLAM.}
\item{Path Planning and Navigation.}
\end{itemize}
}

\divider
\cvachievement{\faCar}{Sensors Fusion Nanodegree - Udacity}{
\href{https://graduation.udacity.com/confirm/GSQ4SS9K}{Certificate} --- \href{https://www.udacity.com/course/sensor-fusion-engineer-nanodegree--nd313}{Description}
\begin{itemize}
\item{Lidar Obstacles Detection, Plane Segmentation and PointsCloud Clustering.}
\item{Camera and Lidar Fusion.}
\item{Radar Obstacle Detection.}
\item{Kalman Filters.}
\end{itemize}
}

\divider

\cvachievement{\faLaptop}{C++ Nanodegree - Udacity}{
\href{https://graduation.udacity.com/confirm/KFNQJGCA}{Certificate} --- \href{https://www.udacity.com/course/c-plus-plus-nanodegree--nd213}{Description}
\begin{itemize}
\item{C++ Foundations.}
\item{Object-Oriented Programming (OOP).}
\item{Memory Management.}
\item{Concurrency.}
\end{itemize}
}


\divider

\cvsection{\large Programming Languages}

\cvtag{C++} 
\cvtag{Python}
\cvtag{Rust}
\cvtag{Java}
\cvtag{MATLAB}
\divider


\cvsection{\large FRAMEWORKS AND LIBRARIES}

% \cvref{name}{email}{mailing address}
\begin{itemize}
\item{ROS/ROS 2}
\item{Eigen3}
\item{g2o}
\item{Ceres}
\item{FLask \& Fast API}
\item{PyBind11}
\item{OpenCV}
\item{Conan The C++ Package Manager}
\end{itemize}
\divider

